---
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
  number_sections: true
 
title: "Creating Wordle in R" 
author: "[User-764Q](https://github.com/User-764Q)"
date: "`r paste0('Last Run: ', format(Sys.time(), '%A %d-%B-%Y'))`"
params: 
  param1: "Don't Forget about params"

---

<style>

#TOC {
 font-family: Calibri; 
 font-size: 16px;
 border-color: #3D68DF;
 background: #3D68DF;
}

body {
  font-family: Garamond;
  font-size: 16px; 
  border-color: #D0D0D0;
  background-color: #D0D0D0;
  color: #1A1A1A;
}

pre {
  color: #1A1A1A
  background: #D0D0D0;
  background-color: #D0D0D0
  font-family: Calibri; 
  
}

</style>


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(collapse = TRUE)

knitr::opts_chunk$set(warning = FALSE)

knitr::opts_chunk$set(message = FALSE)

knitr::opts_chunk$set(include = TRUE)

custom_black <- '1A1A1A'
custom_white <- 'C0C0C0'
custom_grey_dark <- '6F6F6F'
custom_grey_light <- 'B2B2B2'
custom_accent_blue <- '3D6BFF'

```

```{r libraries etc., message = FALSE }

library(gmp)
library(assertive)
library(tidyverse)
library(openxlsx)
library(lubridate)
library(data.table)
library(crayon)

```

### Parameters    

```{r dataload}

Game_Word_Length = 2

Game_Turns_Allowed = 2

```

# Creating Word List for Wordle

### Data Source

I found a list of all Enlish words on GitHub (here)[https://github.com/dwyl/english-words/blob/master/words_alpha.txt]. 

```{r }

raw_word_list <- read_csv('https://github.com/dwyl/english-words/blob/master/words_alpha.txt?raw=true', col_names = 'Word')

```

That list contains 370,102 Words of various lengths, all lower case. 

Wordle is a 5 Letter Word Game so lets filter it to just 5 letter words.

```{r}

Words_x_letters <- raw_word_list %>%
  filter(str_length(Word) == Game_Word_Length)

```

That list contains heaps of words I haven't heard of before so its gonna be a hard 
game, but I can find a list later.

### Is OK entry 

```{r}



```

### Is a word function 

```{r}



```



Making a function to check a candidate word against an answer. 

Needs to take two inputs an answer word and a candidate word. 

And return a data frame with two rows. 

First row is the candidate word (forced to all lower case)

Second row is a * if the letter is in the right place and right letter
+ if the letter is in the word and _ if the letter is not in the word at all. 


```{r}



```


